paper_replication

### 2021-12-16 paper_replication.Rmd
Update paper_replication.Rmd

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#### Large County Function

largecountyanalysis <- function(varname) {
  largecountydem <- countydem %>% filter(Total >= 250000)
  largecountydem <- largecountydem %>% mutate(hasdata = case_when(is.na(largecountydem[[varname]]) ~ 0, 
                                                              !(is.na(largecountydem[[varname]])) ~ 1))
  largecountydemanalysis <- largecountydem %>% filter(hasdata == 1)
  summarytable <- countydem %>% group_by(state) %>% summarize(totalcounties = n())
  usedcounties <- aggregate(largecountydem[[varname]] ~ state, data = largecountydem, function(x) {sum(!(is.na(x)))}, na.action = NULL)
  summarytable <- left_join(summarytable, usedcounties, by = "state")
  # print(summarytable %>% mutate(percent = summarytable[, 3]/totalcounties) %>% kbl(col.names = c("State", "Total Counties", "Counties with Data in 2010", "Percent"), caption = "Table 1. Number of Counties with Data Included in Analysis by State") %>% kable_styling())

  largecountydem$hasdatalabel <- factor(largecountydem$hasdata, levels = c(1, 0), labels = c("Counties in States With Data", "Counties in States Without Data"))

  label(largecountydem$Women) = "Women"
  label(largecountydem$White.pct) = "White"
  label(largecountydem$Black.pct) = "Black"
  label(largecountydem$Native.American.pct) = "Native American"
  label(largecountydem$Asian.pct) = "Asian"
  label(largecountydem$Hispanic.pct) = "Hispanic"
  label(largecountydem$Median.Income) = "Median Income"
  label(largecountydem$College.Grad.pct) = "College Graduates"
  label(largecountydem$percentdem2008) = "Voting for the Democratic candidate in the most recent presidential election"

  units(largecountydem$Women) = "No."
  units(largecountydem$White.pct) = "%"
  units(largecountydem$Black.pct) = "%"
  units(largecountydem$Native.American.pct) = "%"
  units(largecountydem$Asian.pct) = "%"
  units(largecountydem$Hispanic.pct) = "%"
  units(largecountydem$Median.Income) = "$"
  units(largecountydem$College.Grad.pct) = "%"
  units(largecountydem$percentdem2008) = "%"

  # print(table1(~ Women + White.pct + Black.pct + Native.American.pct + Asian.pct + Hispanic.pct + Median.Income + College.Grad.pct + percentdem2008 | hasdatalabel, 
  #      data = largecountydem,
  #     ))

  #calculate propensity scores
  #include education this time
  propensitywts <- glm(hasdata ~ Black.pct + Native.American.pct + Asian.pct + Hispanic.pct + Median.Income + Women + percentdem2008 + College.Grad.pct, data=largecountydem, family=binomial())

  p.score <- predict(propensitywts, largecountydem, type = "response")
  df <- largecountydem
  df$ps <- p.score

  #plot of distribution of propensity scores 
  p1 <- ggplot(df, aes(x = ps, group = hasdatalabel)) + geom_density(aes(fill = hasdatalabel), alpha = 0.2) +
  xlab('Probability of Being in the Analysis') +
  ggtitle('Propensity Score Distribution by Group') +
  scale_fill_discrete('') +
  theme(legend.position = 'bottom', legend.direction = 'vertical') +
  ylab("Density")
  # print(p1)

  #run model
  largecountydemanalysis <- df %>% filter(hasdata == 1)

  model_no_dist <- lm(largecountydemanalysis[[varname]] ~ totalrestrict, data = largecountydemanalysis, weights = ps)

  model_dist <- lm(largecountydemanalysis[[varname]] ~ totalrestrict + distancetoprovider + totalrestrict*distancetoprovider, data = largecountydemanalysis, weights = ps)

returns <- largecountyanalysis("infantdeathrate")
large_county_no_dist <- returns[[1]]
large_county_dist <- returns[[2]]

# Model Summaries
table_7 <- tibble(Characteristic = "Count of Types of Restrictions",
                  Beta = large_county_no_dist$coefficients[2],
                  "p-value" = c('< 0.001')) %>% 
  kbl(caption = "Large County Data: Change in Infant Death Rate per 1000 **** in Model without Distances", 
          digits = 4) %>%
  kable_styling(latex_options = 'hold_position')
table_7

p_2 <- large_county_dist$coefficients[3,4] %>% round(3)
p_3 <- large_county_dist$coefficients[4,4] %>% round(3)

table_8 <- tibble(Characteristic = c("Count of Types of Restrictions", "Distance to Provider",
                                     "Distance/Restriction Interaction"),
                  Beta = c(large_county_dist$coefficients[2], 
                           large_county_dist$coefficients[3],
                           large_county_dist$coefficients[4]),
                  "p-value" = c('< 0.001', p_2, p_3)) %>%
  kbl(caption = "Large County Data: Change in Infant Death Rate per 1000 **** in Model with Distances") %>%
  kable_styling(latex_options = 'hold_position')
table_8

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# largecountyanalysis("Birth.Rate")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# largecountyanalysis("Fertility.Rate")
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# returns <- stateanalysis("AvgAbortionRate2010")
```

@@

p <- model_no_dist$coefficients[2,4] %>% round(3)
# Model Summaries
table_9 <- tibble(Characteristic = "Count of Types of Restrictions",
                  Beta = model_no_dist$coefficients[2],
                  "p-value" = c(p)) %>% 
  kbl(caption = "State Data: Change in Birth Rate Rate per 1000 People in Model without Distances", 
          digits = 4) %>%
  kable_styling(latex_options = 'hold_position')
table_9

@@

p <- model_no_dist$coefficients[2,4] %>% round(3)
# Model Summaries
table_no_dist <- tibble(Characteristic = "Count of Types of Restrictions",
                  Beta = model_no_dist$coefficients[2],
                  "p-value" = c(p)) %>% 
  kbl(caption = "State Data: Change in Fertility Rate Rate per 1000 Women in Model without Distances", 
          digits = 4) %>%
  kable_styling(latex_options = 'hold_position')
table_no_dist

@@

# p <- model_no_dist$coefficients[2,4] %>% round(3)
# Model Summaries
table_no_dist <- tibble(Characteristic = "Count of Types of Restrictions",
                  Beta = model_no_dist$coefficients[2],
                  "p-value" = '< 0.001') %>% 
  kbl(caption = "State Data: Change in Infant Death Rate Rate per 1000 **** in Model without Distances", 
          digits = 4) %>%
  kable_styling(latex_options = 'hold_position')
table_no_dist

>>>>

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
returns <- stateanalysis("AvgAbortionRate2010")
model_no_dist <- returns[[1]]
model_dist <- returns[[2]]

p <- model_no_dist$coefficients[2,4] %>% round(3)
# Model Summaries
table_no_dist <- tibble(Characteristic = "Count of Types of Restrictions",
                  Beta = model_no_dist$coefficients[2],
                  "p-value" = c(p)) %>% 
  kbl(caption = "State Data: Abortion Rate per 1000 Women in Model without Distances", 
          digits = 4) %>%
  kable_styling(latex_options = 'hold_position')
table_no_dist

table_dist <- tibble(Characteristic = c("Count of Types of Restrictions", "Distance to Provider",
                                     "Distance/Restriction Interaction"),
                  Beta = c(model_dist$coefficients[2], 
                           model_dist$coefficients[3],
                           model_dist$coefficients[4]),
                  "p-value" = c(p_1, p_2, p_3)) %>%
  kbl(caption = "State Data: Change in Abortion Rate 1000 Women in Model with Distances") %>%
  kable_styling(latex_options = 'hold_position')
table_dist
```

@@

p <- model_no_dist$coefficients[2,4] %>% round(3)
# Model Summaries
table_9 <- tibble(Characteristic = "Count of Types of Restrictions",
                  Beta = model_no_dist$coefficients[2],
                  "p-value" = c(p)) %>% 
  kbl(caption = "State Data: Change in Birth Rate per 1000 People in Model without Distances", 
          digits = 4) %>%
  kable_styling(latex_options = 'hold_position')
table_9

@@

p <- model_no_dist$coefficients[2,4] %>% round(3)
# Model Summaries
table_no_dist <- tibble(Characteristic = "Count of Types of Restrictions",
                  Beta = model_no_dist$coefficients[2],
                  "p-value" = c(p)) %>% 
  kbl(caption = "State Data: Change in Fertility Rate per 1000 Women in Model without Distances", 
          digits = 4) %>%
  kable_styling(latex_options = 'hold_position')
table_no_dist

@@

# p <- model_no_dist$coefficients[2,4] %>% round(3)
# Model Summaries
table_no_dist <- tibble(Characteristic = "Count of Types of Restrictions",
                  Beta = model_no_dist$coefficients[2],
                  "p-value" = '< 0.001') %>% 
  kbl(caption = "State Data: Change in Infant Death Rate per 1000 **** in Model without Distances", 
          digits = 4) %>%
  kable_styling(latex_options = 'hold_position')
table_no_dist
